Deep Reinforcement Learning for Conservation Decisions

### 2021-06-08 manuscript/manuscript.Rmd
Added some spaces accidentally
Deleting empty lines
Update manuscript/manuscript.Rmd
Co-authored-by: mlap <marcuslapeyrolerie@me.com>

Neural networks become useful in RL when the environment has a large state-action space, which happens frequently with realistic decision-making problems. 
Classic RL algorithms, like policy iteration, value iteration and TD-learning, fail when the state-action space is large, e.g. when the possible states and actions can not be represented in a tractable table [@suttonbarto].
Yet, over the last 10 years, researchers have shown that neural network-based RL algorithms can perform well on previously unsolvable environments [@DQN, @alphaGo2016].
Neural networks have been widely useful in reinforcement learning because neural nets have the property of being general function approximators [@universalapproximators].
Whenever there is a need for an agent to approximate some function, say a policy function or value function, neural networks can be used in this capacity.
While there are other function approximators that can be used in RL, e.g. Gaussian processes [@grande14], neural networks have excelled in this role because of their ability to learn complex, non-linear, high dimensional functions and their ability to adapt given new information [@briefsurveydrl].
We will not discuss in detail how neural networks work [see @lecun_deep_2015], but the general process for how neural networks are used in RL is that at each learning step, the agent, will adjust the parameters in its neural network with which it approximates the policy function and/or value function, so that according to past experiences, the agent will be more likely to engage in highly rewarding behavior in the future. 
This same process occurs in value learning and actor-critic-based deep RL algorithms, except these agents are adjusting either a value network or both a value and policy network respectively

@@

We illustrate the deep RL approach using the algorithm known as Twin Delayed Deep Deterministic Policy Gradient or more simply, TD3 [@TD3].
TD3 is an extension of Deep Deterministic Policy Gradient [DDPG, @DDPG], which itself extended the original Deep Q-Network [DQN, @DQN] algorithm to continuous action space.
A step-by-step walk-through for training both agents on this environment is provided in the Appendix.
We compare the resulting management, policy, and reward under either RL agent to that achieved by the optimal management solution [Fig 2].
Despite having no knowledge of the underlying model, the RL agent learns enough to achieve nearly optimal performance.

>>>>

Neural networks become useful in RL when the environment has a large state-action space, which happens frequently with realistic decision-making problems. 
Classic RL algorithms, like policy iteration, value iteration and TD-learning, fail when the state-action space is large, e.g. when the possible states and actions can not be represented in a tractable table [@suttonbarto].
Yet, over the last 10 years, researchers have shown that neural network-based RL algorithms can perform well on previously unsolvable environments [@DQN, @alphaGo2016].
Neural networks have been widely useful in reinforcement learning because neural nets have the property of being general function approximators [@universalapproximators].
Whenever there is a need for an agent to approximate some function, say a policy function or value function, neural networks can be used in this capacity.
While there are other function approximators that can be used in RL, e.g. Gaussian processes [@grande14], neural networks have excelled in this role because of their ability to learn complex, non-linear, high dimensional functions and their ability to adapt given new information [@briefsurveydrl].
We will not discuss in detail how neural networks work [see @lecun_deep_2015], but the general process for how neural networks are used in RL is that at each learning step, the agent, will adjust the parameters in its neural network with which it approximates the policy function and/or value function, so that according to past experiences, the agent will be more likely to engage in highly rewarding behavior in the future.

@@

We illustrate the deep RL approach using the algorithm known as Twin Delayed Deep Deterministic Policy Gradient or more simply, TD3 [@TD3].
TD3 is an extension of Deep Deterministic Policy Gradient [DDPG, @DDPG], which itself extended the original Deep Q-Network [DQN, @DQN] algorithm to continuous action space.
A step-by-step walk-through for training agents on this environment is provided in the Appendix.
We compare the resulting management, policy, and reward under either RL agent to that achieved by the optimal management solution [Fig 2].
Despite having no knowledge of the underlying model, the RL agent learns enough to achieve nearly optimal performance.
